---
title: "03-analyse"
format: html
---

Source and licence: Data comes from \[https://github.com/KeithGalli/Olympics-Dataset/tree/master\] and uses the MIT License

What is in it: 145500 rows/athletes, 10 columns / variables, the variables and example data can be read here:

```{r}
head(bios)
```

## Research questions:

1.  Descriptive: Which citys per country are the athletes most likely to be born
2.  Descriptive: Mean BMI of the athletes
3.  Descriptive: How the athletes (e.g. their weight) changed over time
4.  Explanatory: Does born_country influence weight/height?

## Context and target audience

Potentially journalistic, reporting about the changes over time regarding the participants of the olympic games, or a sports scientist interested in finding out whether a young talent is a typical athlete.

## Initial data analysis

```{r}
glimpse(bios)
```

### Height

```{r}
bios %>%
  summarise(
    mean_height = mean(height_cm, na.rm = TRUE),
    median_height = median(height_cm, na.rm = TRUE),
    min_height = min(height_cm, na.rm = TRUE),
    max_height = max(height_cm, na.rm = TRUE),
    amount_NA = sum(is.na(height_cm))
  )
```

### Weight

```{r}
bios %>%
  summarise(
    mean_weight = mean(weight_kg, na.rm = TRUE),
    median_weight = median(weight_kg, na.rm = TRUE),
    min_weight = min(weight_kg, na.rm = TRUE),
    max_weight = max(weight_kg, na.rm = TRUE),
    amount_NA = sum(is.na(weight_kg))
  )
```

### Plot Height - Weight

```{r}
bios %>%
  ggplot(aes(x = weight_kg, y = height_cm)) +
  geom_point() +
  geom_smooth(method = "lm")
```

### Plot showing height distribution

```{r}
bios %>%
  ggplot(aes(x = height_cm)) +
  geom_histogram(bins = 30)
```

## Quality Issues

Just looking at height and weight, we already have accumulated \~80000 missing values.

Also we have many string variables, which aren't very easy to present and summarize.
